Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-04-29 research_proposal/research_proposal.qmd
poet and novelist-pc approach

-   POET
-   Novelist with PC-adjusted

>>>>

***(c) POET***

The POET (Principal Orthogonal complEment Thresholding) estimator, proposed by Fan et al. (2013), is another "sparse" + "non-sparse" covariance estimator. It starts by decomposing the correlation matrix $\hat{\boldsymbol{R}}_1$ into a prominent principle components part (low-rank) and a orthogonal complement part $\hat{\boldsymbol{R}}_{1, K}$ (the correlation matrix after removing the first $K$ principal components). Then it applies thresholding to $\hat{\boldsymbol{R}}_{1, K}$. The POET estimator is given by:

$$
\hat{\boldsymbol{R}}^{K}_{1} = \sum_{k = 1}^K \hat{\gamma}_k \hat{\boldsymbol{\xi}}_k \hat{\boldsymbol{\xi}}_k' + T(\hat{\boldsymbol{R}}_{1, K})
$$

where $\hat{\gamma}_k$ and $\hat{\boldsymbol{\xi}}_k$ are the $k$th eigenvalue and eigenvector of the sample covariance matrix. $T(.)$ is the thresholding function, which can be either soft-thresholding, hard-thresholding, or others.

***(d) NOVELIST with PC-adjusted***

This approach is similar to the POET estimator. The difference is that POET apply thresholding to the orthogonal complement part $\hat{\boldsymbol{R}}_{1, K}$, meanwhile we apply NOVELIST. It can be formulated as:

$$
\hat{\boldsymbol{R}}^{N, K}_{1} = \sum_{k = 1}^K \hat{\gamma}_k \hat{\boldsymbol{\xi}}_k \hat{\boldsymbol{\xi}}_k' + \hat{\boldsymbol{R}}^{N}_{1, K}
$$

and $\hat{\boldsymbol{R}}^{N}_{1, K}$ is the NOVELIST estimator applied to the orthogonal complement part $\hat{\boldsymbol{R}}_{1, K}$.
